The \dealii Library, Version 9.5

### 2023-06-16 9.5/paper.tex

\hypersetup{
  pdfauthor={
    Daniel Arndt,
    Wolfgang Bangerth,
    Maximilian Bergbauer,
    Marc Fehling,
    Timo Heister,
    Luca Heltai,
    Martin Kronbichler,
    Matthias Maier,
    Peter Munch,
    Jean-Paul Pelteret,
    Bruno Turcksin,
    David Wells
  },
  pdftitle={The deal.II Library, Version 9.5, 2023},
}

@@

\author[5]{Timo~Heister}
 \affil[5]{School of Mathematical and Statistical Sciences,
   Clemson University,
   Clemson, SC, 29634, USA
   {\texttt{heister@clemson.edu}}}

\author[6]{Luca~Heltai}
\affil[6]{SISSA,
   International School for Advanced Studies,
   Via Bonomea 265,
   34136, Trieste, Italy.
   {\texttt{marco.feder/luca.heltai@sissa.it}}}

 \author[7]{Martin~Kronbichler}
 \affil[7]{Institute of Mathematics,
   University of Augsburg,
   Universit\"atsstr.~12a, 86159 Augsburg, Germany.
   {\texttt{martin.kronbichler/peter.muench@uni-a.de}}}

\author[8]{Matthias~Maier}
\affil[8]{Department of Mathematics,
  Texas A\&M University,
  3368 TAMU,
  College Station, TX 77845, USA.
  {\texttt{maier@math.tamu.edu}}}

\author[7,9]{Peter Munch}
 \affil[9]{Institute of Material Systems Modeling,
 Helmholtz-Zentrum Hereon,
 Max-Planck-Str. 1, 21502 Geesthacht, Germany}

\author[10]{Jean-Paul~Pelteret}
\affil[10]{Independent researcher.
{\texttt{jppelteret@gmail.com}}}

@@

>>>>

\hypersetup{
  pdfauthor={
    Daniel Arndt,
    Wolfgang Bangerth,
    Maximilian Bergbauer,
    Marc Fehling,
    Marco Feder,
    Johannes Heinz,
    Timo Heister,
    Luca Heltai,
    Martin Kronbichler,
    Matthias Maier,
    Peter Munch,
    Jean-Paul Pelteret,
    Bruno Turcksin,
    David Wells
  },
  pdftitle={The deal.II Library, Version 9.5, 2023},
}

@@

\author[5]{Marco~Feder}
\affil[5]{SISSA,
International School for Advanced Studies,
Via Bonomea 265,
34136, Trieste, Italy.
{\texttt{marco.feder/luca.heltai@sissa.it}}}

\author[6]{Johannes~Heinz}
 \affil[6]{Institute of Mechanics and Mechatronics,
   TU Wien,
   Getreidemarkt 9, 1060 Vienna, Austria
   {\texttt{johannes.heinz@tuwien.ac.at}}}

\author[7]{Timo~Heister}
 \affil[7]{School of Mathematical and Statistical Sciences,
   Clemson University,
   Clemson, SC, 29634, USA
   {\texttt{heister@clemson.edu}}}

\author[5]{Luca~Heltai}

 \author[8]{Martin~Kronbichler}
 \affil[8]{Institute of Mathematics,
   University of Augsburg,
   Universit\"atsstr.~12a, 86159 Augsburg, Germany.
   {\texttt{martin.kronbichler/peter.muench@uni-a.de}}}

\author[9]{Matthias~Maier}
\affil[9]{Department of Mathematics,
  Texas A\&M University,
  3368 TAMU,
  College Station, TX 77845, USA.
  {\texttt{maier@math.tamu.edu}}}

\author[8,10]{Peter Munch}
 \affil[10]{Institute of Material Systems Modeling,
 Helmholtz-Zentrum Hereon,
 Max-Planck-Str. 1, 21502 Geesthacht, Germany}

\author[11]{Jean-Paul~Pelteret}
\affil[11]{Independent researcher.
{\texttt{jppelteret@gmail.com}}}

@@

J.~Heinz was supported by the European Union’s Framework Programme for Research
and Innovation Horizon 2020 (2014-2020) under the Marie Sk\l{}odowska--Curie Grant
Agreement No. [812719].
